---
title: "Assignment - KNN Occupancy"
author:
  - name author here - Omercan Gurbuz
  - name reviewer here - Aziz
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---
## Setup your library

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
library("ggplot2")
```

---

## Choose a suitable dataset 
from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.


## Business Understanding
A hospital wants to know if patients who have been checked out are still counted as occupying hospital rooms. They want a model that will allow them to determine whether there is someone in the room based on real-time data from their hospital rooms. Regardless of what time of the year it is.

## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
view(rawDF)
```

## Data Preparation

```{r}
model1<-lm( Occupancy ~ Light + Humidity + Temperature + date + HumidityRatio,data=rawDF)
summary(model1)
```

```{r}
cleanDF <- rawDF[c(-1,-2,-3,-10)]
head(cleanDF)
```

#We convert the occupancy variable into a factor since many models call for the variable we wish to focus on to be a factor.

```{r}
cntOccu <- table(cleanDFOccupancy)
propOccu <- round(prop.table(cntOccu) * 100 , digits = 1)
cleanDFOccupancy <- factor(cleanDFOccupancy, levels = c(0, 1))
```

#To test whether the knn function is successful in predicting occupancy based on light and CO2, we divide the data twice: once to train it and once to test it.

```{r}
trainDF_feat <- cleanDF[1:4071,  ]
testDF_feat <- cleanDF[4072:8143,  ]
trainDF_labels <- cleanDF[1:4071,  3]
testDF_labels <- cleanDF[4072:8143,  3]

```


## Modeling

#Finally, training and presenting our model is what remains.
```{r}
cleanDF_occupancy_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_occupancy_pred)


```



## Evaluation and Deployment

```{r}
confusionMatrix(cleanDF_occupancy_pred, testDF_labels[[0]], positive = NULL, dnn = c("Prediction", "True"))
```


## Evaluation and Deployment

reviewer adds suggestions for improving the model