---
title: "Assignment - KNN Occupancy"
author:
  - name author here - Omercan Gurbuz
  - name reviewer here - Aziz
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---
## Setup your library

```{r}
library(tidyverse)
library(googlesheets4)
library(class)
library(caret)
library("ggplot2")
```

---

## Choose a suitable dataset 
from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train  your own kNN model. Follow all the steps from the CRISP-DM model.


## Business Understanding
A hospital wants to know if patients who have been checked out are still counted as occupying hospital rooms. They want a model that will allow them to determine whether there is someone in the room based on real-time data from their hospital rooms. Regardless of what time of the year it is.

## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/assignments/master/datasets/KNN-occupancy.csv"
rawDF <- read_csv(url)
view(rawDF)
```
#Seven factors in the shown data are related to hospital rooms. We must first examine the values that link to occupancy while taking temperature and date into account because the model we want to build needs to function regardless of the season.


## Data Preparation
#We must first determine which factor significantly correlates with a room's occupancy. To ensure that other factors aren't affecting the connection, we do this by creating a model and accounting for the other variables.
```{r}
model1<-lm( Occupancy ~ CO2 + Light + Humidity + Temperature + date + HumidityRatio,data=rawDF)
summary(model1)
```

#This demonstrates that everything, with the exception of humidity, is related to occupancy. We will base or base our model on CO2 and Light as Temperature can vary greatly with the seasons and Date has a limited correlation to occupancy. We shall eliminate the other factors from the data for this.
 

```{r}
cleanDF <- rawDF[c(-1,-2,-3,-6)]
head(cleanDF)
```

#We convert the occupancy variable into a factor since many models call for the variable we wish to focus on to be a factor.

```{r}
cntOccu <- table(cleanDF$Occupancy)
propOccu <- round(prop.table(cntOccu) * 100 , digits = 1)
cleanDF$Occupancy <- factor(cleanDF$Occupancy, levels = c(0, 1))
```

#To test whether the knn function is successful in predicting occupancy based on light and CO2, we divide the data twice: once to train it and once to test it.

```{r}
trainDF_feat <- cleanDF[1:4071,  ]
testDF_feat <- cleanDF[4072:8143,  ]
trainDF_labels <- cleanDF[1:4071,  3]
testDF_labels <- cleanDF[4072:8143,  3]

```


## Modeling

#Finally, training and presenting our model is what remains.
```{r}
cleanDF_occupancy_pred <- knn(train = as.matrix(trainDF_feat), test = as.matrix(testDF_feat), cl = as.matrix(trainDF_labels), k = 21)
head(cleanDF_occupancy_pred)


```



## Evaluation and Deployment

```{r}
confusionMatrix(cleanDF_occupancy_pred, testDF_labels[[1]], positive = NULL, dnn = c("Prediction", "True"))
```
#As you can see, our algorithm is surprisingly accurate—especially when it comes to determining if a room is actually empty—missing the mark just 2 times out of 3462 predictions. This is fantastic since you won't have to deal with the hassle of having a program turn the lights out in the workspace. This precaution does come with a minor cost, since the model was 24 times out of the 610 times it predicted there would be someone in the room, which might add up to a significant electricity expense if the model was used to control the lights.

## Evaluation and Deployment

reviewer adds suggestions for improving the model