---
title: "Naive Bayes Assignment 2"
author:
  - name author - Aziz Abbas
  - name reviewer here - Omercan Gurbuz
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
   html_notebook:
    toc: true
    toc_depth: 2
---



```{r}
install.packages("tidyverse")
install.packages("tm")            #for text mining 
install.packages("wordcloud")
install.packages("e1071")
install.packages("RColorBrewer")  #for color palettes

library(tidyverse)
library(tm)
library(caret)
library(wordcloud)
library(e1071)
library(cd)
library(class)
library(magrittr)                 #needs to run evertyime you start R and want the use %>%  symbol
library(dplyr)
library(RColorBrewer)
library(corpus)
---
  
  Choose a suitable dataset from [this](https://github.com/HAN-M3DM-Data-Mining/assignments/tree/master/datasets) folder and train your own Naive Bayes model. Follow all the steps from the CRISP-DM model.


## Business Understanding
```{r}
#The data set contains a compilation of fake and real news. #This model is to predict if the news are real or fake. 
```


## Data Understanding
```{r}
url <- "https://raw.githubusercontent.com/HAN-M3DM-Data-Mining/data-mining-s1y2223-ghost/master/datasets/NB-fakenews.csv"
rawdata <- read.csv(url)
```

```{r}
## Data Preparation
rawdata <- rawdata[-1]
rawdata <- rawdata[-1]
rawdata <- rawdata[-1]

```

```{r}
#To transform data from digits of 0 and 1 to the words "Fake" and "True" use the follow code

rawdata <- mutate(rawdata,label = recode(label,"0" = "True","1" = "Fake"))

rawdata$label <- rawdata$label %>%  factor %>% relevel("Fake")
class(rawdata$label)
```

```{r}
#Filter the Real and Fake data apart from each other
Real <- rawdata %>% filter(label == "Real")
Fake <- rawdata %>% filter(label == "Fake")
```


```{r}
#Show highly used words in the articles 

wordcloud(Real$text,max.words = 200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Dark2")) 
          
wordcloud(Fake$text,max.words = 200, random.order=FALSE, rot.per=0.35, 
          colors=brewer.pal(8, "Set2"))
```

```{r}
#Make the raw corpus 
rawCorpus <- Corpus(VectorSource(rawdata$text))
inspect(rawCorpus[1:3])
```

```{r}
#Make all the characters lowercase
tolower(rawCorpus)
```


```{r}
#Remove all punctuation marks
removePunctuation(rawCorpus)
```

```{r}
#Remove all the numbers
removeNumbers(rawCorpus)
```


```{r}
#Remove excess whitespace
stripWhitespace(rawCorpus)

```

```{r}
#Remove the stopwords
removestopwords(rawCorpus)
```

```{r}
#Create Document Term Matrix to count all the words
#Will take some time to load
cleanDTM <- rawCorpus %>% DocumentTermMatrix()
inspect(cleanDTM)
```

```{r}
#Inserting the random number generator (RNG)
set.seed(123)
```

```{r}
DataPartion <- createDataPartition(rawdata$label, p=99, list = FALSE, times = 1)
head(DataPartion)
```

```{r}
trainCorpus <- cleancorpus[trainIndex]
testCorpus <- cleancorpus[-trainIndex]
trainDTM <- cleanDTM2[trainIndex, ]
testDTM <- cleanDTM2[-trainIndex, ]
```

```{r}
#Creating a matrix with the words
convert_counts <- function(x) {
  x <- ifelse(x > 0, 1, 0) %>% factor(levels = c(0,1), labels = c("no", "yes"))
}
```

```{r}
nColsDTM <- dim(trainDTM)[2]
trainDTM <- apply(trainDTM, MARGIN = 2, convert_counts)
testDTM <- apply(testDTM, MARGIN = 2, convert_counts)

head(trainDTM[,1:10])
```

```{r}
#creating the model 
nbayesModel <-  naiveBayes(trainDTM, trainDF$label, laplace = 1)
predVec <- predict(nbayesModel, testDTM)
confusionMatrix(predVec, testDF$label, positive = "1", dnn = c("Prediction", "True"))
```

## Evaluation and Deployment

#Line 35 missing "##" to turn it into a comment


#Line 39 missing "the end of the r syntax "```{r}" it will cause problem when reading. 

## Line 69 changes the label into true and not Real. 

## Line 77 has an error because the occurance of Real is 0. the label should be fixed for the model to work. 

